Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@

63\% of all constraint violations are caused by warning constraints which are only 10\% of all constraints. 
Only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.

\begin{hyp}
Data quality is good since only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.
The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
\end{hyp}

80\% of the \emph{QB} constraints are error constraints.
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are informational constraints.
For Disco, 1/6 of the constraint violations are caused by error constraints.
Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are warnings.  
\begin{hyp}
In general, data quality is very high.
The quality of data represented by established vocabularies is good,
as serious constraint violations rarely appear.
The quality of data represented by newly developed vocabularies, however, is worse,
as serious constraint violations occur partially.
\end{hyp}

>>>>

63\% of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.

\begin{hyp}
In general, data quality is high (according to severity levels) since only 6\% of the violations are caused by error constraints which are 49\% of all defined constraints.
\end{hyp}

\begin{hyp}
The percentage of severe violations is very low (6\%), compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
\end{hyp}

@@

80\% of the \emph{QB} constraints are error constraints.
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are informational constraints.
1/6 of the Disco violations are caused by error constraints.
Almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by warning constraints.  
\begin{hyp}
For established vocabularies, the data quality is high,
as serious violations rarely appear.
For newly developed vocabularies, data quality is worse,
as serious violations occur partially.
\end{hyp}
